Coherent optical association of a single molecule -- Supplemental material

### 2020-12-02 paper.tex
Update on Overleaf.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
8 excited molecular state potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
and the continuum~\cite{Liu2017}.
This calculation shows that $\Omega_R/\Gamma_s$
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
see Supplementary Material for details.
As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
as the closest intermediate state to drive the Raman transition.

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
we use the tweezer beam itself as the Raman beams by turning on two frequencies
in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
The dual use of the tweezer beam not only eliminates additional scattering sources
or undesired laser frequencies,
but also allows a tight focus to maximize the Raman Rabi frequency
and minimize the transfer time.
Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
to filter the laser spectrum generated by a fiber amplifier
that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
We observe a reduction of the scattering rate by a factor of $2$
due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
that couples to other excited states.
After the total tweezer power is set to the desired value,
we smoothly ramp down the power of one frequency in the tweezer
while simultaneously ramping up the power of the other frequency
so that the total tweezer power remains unchanged.
Both frequencies are kept on for a specified duration before the process is reversed
and the tweezer returns to a single frequency.

@@

The efficiency of the transfer is lower than expected
because we found the ratio of the molecular scattering rate~(i.e. inverse of lifetime)
to the Rabi frequency is 10 times larger than predicted.
If this discrepancy arises from the $v'=0$ excited state,
it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to$a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a_P$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|}
    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $40~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
$2\pi\times 5.5(2)~\mathrm{MHz}$.
This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $63(3)$ & $77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}

With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
we now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.

>>>>

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
8 excited molecular potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
and the continuum~\cite{Liu2017}.
This calculation shows that $\Omega_R/\Gamma_s$
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
see Supplementary Material for details.
As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
as the closest intermediate state to drive the Raman transition.

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
we use the tweezer beam itself as the Raman beams by turning on two frequencies
in the tweezer during the Raman pulse using an acousto-optic modulator, as shown in Fig.~\ref{f-beampath}.
The dual use of the tweezer beam not only eliminates additional scattering sources
or undesired laser frequencies,
but also allows a tight focus to maximize the Raman Rabi frequency
and minimize the transfer time.
Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
to filter the laser spectrum. 
As shown in Fig.~\ref{f-beampath}, we place one filter directly after the laser, which is a fiber amplifer seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We place the second filter as close to the microscope objective as possible. 
We observe a reduction of the scattering rate by a factor of $2$
due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
that couples to other excited states.
After the total tweezer power is set to the desired value,
we smoothly ramp down the power of one frequency in the tweezer
while simultaneously ramping up the power of the other frequency
so that the total tweezer power remains unchanged.
Both frequencies are kept on for a specified duration before the process is reversed
and the tweezer returns to a single frequency.

@@

The efficiency of the transfer is lower than expected
because we found the ratio of the molecular scattering rate~(i.e. inverse of lifetime)
to the Rabi frequency is 10 times larger than predicted.
This discrepancy can arise from the $v'=0$ excited state, if the ratio $\Omega_m / \Omega_a$ or $\Gamma_e$ are larger than expected.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweezer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a_P$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz\cdot GHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|}
    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

To determine $\Omega_m$ and $ \Omega_a$, we measure the change in resonance frequency and Raman Rabi frequency as a function of the tweezer detuning. 
For both these quantities, we observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a, b.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling to the $v'=0$ intermediate state. Combining the fit coefficients, summarized in Table \ref{tab:f-det:fit}, for the $1/\Delta$ component, we can extract $\Omega_m $ and $ \Omega_a $.

We perform the experiment at various tweezer powers to extract the power dependence of $ \Omega_m $ and $ \Omega_a $, as shown in Fig.~\ref{f-det}c. $ \Omega_m $ scales with $ P^{0.5} $ as expected, and we obtain a fit value of $2\pi\times180.87(7)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $40~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. The scaling of $ \Omega_a $ differs from $ P^{0.5} $, which is the expected scaling from the laser intensity, due to the change in the atomic wavefunction caused by tighter confinement at higher power. For weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment. Thus, $ \Omega_a $ scales as $ P^{0.79} $, which fits well to our experimental result.
The fit value is $2\pi\times1.85(3)~\mathrm{MHz}/\mathrm{P^{0.79}}$. At $3.75~\mathrm{mW}$ tweezer power, we measured $ \Omega_m = 2\pi \times 348.3(3)~\mathrm{MHz}$ and $ \Omega_a = 2\pi\times 5.5(2)~\mathrm{MHz}$, resulting in a $ \Omega_m/\Omega_a$ ratio of about $ 63 $, which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, the matrix element ratio is not the cause of our lower than expected transfer efficiency.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
%We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
% From these measurements, we can extract a $\Omega_m$ of

%In order to calculate the ratio $\Omega_m/\Omega_a$,
%we now need to extract $ \Omega_a $.
%We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
%The Raman Rabi frequency shows a non-linear dependency on the tweezer power
%due to the change in the atomic wavefunction caused by
%tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.

%Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
%which fits well to our experimental result, as shown in Fig.~\ref{f-det}b.
%Similar to the light shift, the detuning dependency of the Raman Rabi frequency
%is determined by a constant background component and
%a $v'=0$ component that scales as $1/\Delta$.
%The $v'=0$ component of the Raman Rabi frequency at our detuning is
%$2\pi\times1.10(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
%or $2\pi \times 6.08(9)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ %tweezer power.
%Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
%$2\pi\times 5.5(2)~\mathrm{MHz}$.
%This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $63(3)$,
%which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $2\pi \times 3.28(4)~\mathrm{kHz}$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $2\pi \times 0.80(4)~\mathrm{kHz}$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $\Omega_m$ & $2\pi \times 348.3(3)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 5.5(2)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $63(3)$ & $77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $151~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}

%With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
We now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.

### 2020-12-02 sm.tex
[sm] let's just call it red line...
Update on Overleaf.

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
  \caption{Full calculation of the Raman Rabi frequency and scattering rate
    as a function of the single-photon frequency
    including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$
    and the atomic continuum.
    The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$
    and resonant with the two photon transition.
    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
    The thick red line shows the contribution that comes only from the near-threshold states.
    \label{f-sm}}
\end{figure}

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/fcf_c3sigma.pdf}
  \caption{The Franck-Condon Factor (FCF) between the target molecular state and vibrational state $v'$ of $c^3\Sigma^+_1$. The potential supports 74 bound states, and the predominant contribution arises from the near-threshold bound states. The total overlap with all the bound states is $0.4822$, which is $96.8\%$ of the total triplet fraction of the target molecular state.
    \label{f-smfcf}}
\end{figure}

>>>>

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
  \caption{Full calculation of the Raman Rabi frequency and scattering rate
    as a function of the single-photon frequency
    including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$
    and the atomic continuum.
    The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$
    and resonant with the two photon transition.
    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
    The red line shows the contribution that comes only from the near-threshold states.
    \label{f-sm}}
\end{figure}

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/fcf_c3sigma.pdf}
  \caption{The Franck-Condon Factor (FCF) between the target molecular state and vibrational state $v'$ of $c^3\Sigma^+_1$. The potential supports 74 bound states, and the predominant contribution arises from the near-threshold bound states. The total overlap with all the bound states is $0.4822$, which is $96.8\%$ of the total triplet fraction of the target molecular state.
    \label{f-smfcf}}
\end{figure}
\section{Effective Matrix Elements to a Single State}

In this calculation, there is a matrix element, $\Omega_{ai}, \Omega_{mi}$ between each channel $ i $ of the coupled channel ground state and an excited state. The total Raman Rabi frequency $ \Omega_R$, light shift $ \delta$ and off-resonant scattering $ \Gamma_S $ contribution from this single excited state is calculated as

\begin{align}
    \Omega_{R} &= \displaystyle\sum_{i} \frac{\Omega_{ai} \Omega_{mi}}{2\Delta} \\
    \delta &= \displaystyle\sum_{i} \frac{\Omega_{ai}^2 - \Omega_{mi}^2}{2\Delta} \\
    \Gamma_S &= \displaystyle\sum_{i} \Gamma_e \frac{\Omega_{ai}^2 + \Omega_{mi}^2}{2\Delta^2}
\end{align}

where $ \Delta $ is the single photon detuning and $ \Gamma_e $ is the excited state linewidth. The experiment, through measuring the detuning dependence of the Raman Rabi frequency and the resonance frequency, extracts a single $ \Omega_m $ and $ \Omega_a $. In order to compare to the theory, we introduce effective $ \Omega_a', \Omega_m', \Gamma_e'$, so that $ \Omega_R = \Omega_a'\Omega_m'/2\Delta $, $\delta = (\Omega_{a}'^2 - \Omega_{m}'^2)/2\Delta $, and $\Gamma_S = \Gamma_e'(\Omega_{a}'^2 + \Omega_{m}'^2)/2\Delta^2 $. These effective Rabi frequencies are used to calculate the Rabi frequency ratio and are the quantities reported in the main text when compared to experiment.

\section{Scaling of atomic matrix element with tweezer power}
